---
title: "Reproducibility Report"
output:
  html_document:
    toc: true
    toc_float: true
---

# Report Details

```{r}
articleID <- 6-7-2014 # insert the article ID code here e.g., "10-3-2015"
reportType <- "pilot" # specify whether this is the 'pilot' report or 'copilot' report
pilotNames <- "Ashish Mehta" # insert the pilot's name here e.g., "Tom Hardwicke".
copilotNames <- "Kayla Good" # # insert the co-pilot's name here e.g., "Michael Frank".
pilotTTC <- 180 # insert the pilot's estimated time to complete (in minutes, it is fine to approximate) e.g., 120
copilotTTC <- NA # insert the co-pilot's estimated time to complete (in minutes, it is fine to approximate) e.g., 120
pilotStartDate <- as.Date("11/01/19", format = "%m/%d/%y") # insert the piloting start date in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
copilotStartDate <- NA # insert the co-piloting start date in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
completionDate <- NA # insert the date of final report completion in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
```

------

#### Methods summary: 

Two-hundred-two volunteers at a subway station on either the westbound (n = 101) or eastbound (n = 101) platform were asked to rate the subjective distance of another subway station on the line they are traveling, (either coming up or just past). Participants were randomly assigned to conditions where they rate distance of stations either: 2 stops west, 1 stop west, 1 stop east, or 2 stops east. Participants were asked how far away each station felt on a 1-7 scale.

------

#### Target outcomes: 

For this article you should focus on the findings reported in the results section of Experiment 1.

Specifically, you should attempt to reproduce all descriptive and inferential analyses reported in the text below and associated tables/figures:

> Results

> We carried out a 2 (orientation: toward, away from) × 4 (station: Spadina, St. George, Bloor-Yonge, Sherbourne) analysis of variance (ANOVA) on closeness ratings, which revealed no main effect of orientation, F < 1, and a main effect of station, F(3, 194) = 24.10, p < .001, ηp2 = .27. This main effect was qualified by the predicted interaction between orientation and station, F(3, 194) = 16.28, p < .001, ηp2 = .20. We decomposed this interaction by the subjective-distance ratings between participants traveling east and west for each of the four subway stations. Westbound participants rated the stations to the west of Bay Street as closer than did eastbound participants; this effect was obtained for both the station one stop to the west (St. George, p < .001, ηp2 = .28) and the station two stops to the west (Spadina, p = .001, ηp2 = .20). The opposite pattern held true for stations to the east of Bay Street. Eastbound participants rated the stations to the east of Bay Street as closer than did westbound participants; this effect was obtained for both the station one stop to the east (Bloor-Yonge, p = .053, ηp2 = .08) and the station two stops to the east (Sherbourne, p < .001, ηp2 = .24). Figure 1 summarizes these results. comparing

**Note**
Make sure to use the original article for additional context and information about any necessary pre-processing steps. Also check for additional supplementary materials that may provide supporting documentation for analysis procedures.
  

------


```{r global_options, include=FALSE}
# sets up some formatting options for the R Markdown document
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
options(digits = 3)
```

# Step 1: Load packages and prepare report object


```{r}
# load packages
library(tidyverse) # for data munging
library(knitr) # for kable table formating
library(haven) # import and export 'SPSS', 'Stata' and 'SAS' Files
library(readxl) # import excel files
library(ReproReports) # custom reporting functions
library(lsr) # calculate partial eta squared
library(here) # root file path
library(pander)
```


```{r}
# Prepare report object. This will be updated automatically by the reproCheck function each time values are compared
reportObject <- data.frame(dummyRow = TRUE, reportedValue = NA, obtainedValue = NA, valueType = NA, percentageError = NA, comparisonOutcome = NA, eyeballCheck = NA)
```

# Step 2: Load data

```{r}
df_raw <- read_excel(here("GroupB_6-7-2014/data/S1_Subway.xlsx"))
```

# Step 3: Tidy data

Reordering the factor to match the plot in the paper
```{r}
EAST_STNS <- c("B-Y", "SHER")
WEST_STNS <- c("STG", "SPAD")

df <- df_raw %>%
  mutate(STN_NAME = factor(STN_NAME, levels = c("SPAD", "STG", "B-Y", "SHER")))
  

```

# Step 4: Run analysis

## Pre-processing

Creating a variable for orientation (whether participants are facing toward or away from the station they are responding about).
```{r}
df <- df %>% 
  mutate(
    ORIENTATION = case_when(
      DIRECTION == "EAST" & STN_NAME %in% EAST_STNS ~ "TOWARD",
      DIRECTION == "WEST" & STN_NAME %in% WEST_STNS ~ "TOWARD",
      DIRECTION == "WEST" & STN_NAME %in% EAST_STNS ~ "AWAY",
      DIRECTION == "EAST" & STN_NAME %in% WEST_STNS ~ "AWAY")
  )
  
```

## Descriptive statistics

Grand mean and descriptives
```{r}
df %>%
  summarize(mean = mean(DISTANCE),
            sd = sd(DISTANCE),
            n = n(),
            se = sd/sqrt(n)) %>% 
  kable
```

Descriptives by station name
```{r}
df %>% 
  group_by(STN_NAME) %>% 
  summarize(mean = mean(DISTANCE),
            sd = sd(DISTANCE),
            n = n(),
            se = sd/sqrt(n))%>% 
  kable
```

Descriptives by direction facing
```{r}
df %>% 
  group_by(DIRECTION) %>% 
  summarize(mean = mean(DISTANCE),
            sd = sd(DISTANCE),
            n = n(),
            se = sd/sqrt(n))%>% 
  kable
```

Descriptives by orientation in relation to target
```{r}
df %>% 
  group_by(ORIENTATION) %>% 
  summarize(mean = mean(DISTANCE),
            sd = sd(DISTANCE),
            n = n(),
            se = sd/sqrt(n))%>% 
  kable
```

Reproducing the plot from the paper
```{r}
df %>% 
  ggplot(aes(x = STN_NAME, y = DISTANCE, color = DIRECTION)) +
  stat_summary(fun.data="mean_se") + 
  scale_y_continuous(breaks = seq(0,5,.25)) +
  theme_minimal()
```

Standard error bars were off in the previous plot, so now checking if maybe they're supposed to be 95% CI bars. It almost looks like it could be right, but it's hard to tell since the y-axis in the paper does not have tick marks.
```{r}
df %>% 
  group_by(DIRECTION, STN_NAME) %>% 
  summarize(
    N = n(),
    SE = sd(DISTANCE)/sqrt(N),
    CI = SE*qt(.025, N-1),
    DISTANCE = mean(DISTANCE)
  ) %>% 
  ggplot(aes(x = STN_NAME, y = DISTANCE, color = DIRECTION)) +
  geom_pointrange(aes(ymin = DISTANCE - CI, ymax = DISTANCE + CI), 
                  position = position_jitter(.1)) + 
  scale_y_continuous(breaks = seq(0,5,.25)) +
  theme_minimal()
```

## Inferential statistics

This is the main model from the study. Using a 2x2 anova, the authors and I found the predicted interaction between direction and station. This was confusing because the authors mislabeled the their model terms. In the paper the authors state that they ran a "2 (orientation: toward, away from) × 4 (station: Spadina, St. George, Bloor-Yonge, Sherbourne) analysis of variance (ANOVA) on closeness ratings", when in fact they ran a 2 (direction: east, west) × 4 (station: Spadina, St. George, Bloor-Yonge, Sherbourne) ANOVA on closeness ratings. 
```{r}
s_direction <- summary(fit_direction <- aov(DISTANCE ~ DIRECTION*STN_NAME, data = df))
pander((etasqrd <- etaSquared(fit_direction)))
pander(fit_direction)
```
When running this ANOVA, the results match for the most part although the F-value is off by `r 24.1 - s_direction[[1]][2,4]`.



Now I have tried try running the model again using a type 3 ANOVA. This time I get the correct F-value from the paper.
```{r}
fit_final <- car::Anova(lm(DISTANCE ~ DIRECTION * STN_NAME, data=df,
              contrasts=list(DIRECTION=contr.sum, STN_NAME=contr.sum)), type=3)

pander(fit_final)
```


Here is the ANOVA that they say they ran. The values do not match with the paper.
```{r}
summary(fit_orientation <- aov(DISTANCE ~ ORIENTATION*STN_NAME, data = df))
pander(etaSquared(fit_orientation))
pander(fit_orientation)
```


Here are the post-hoc pairwise comparisons for each station
```{r}
df %>% 
  split(.$STN_NAME) %>% 
  map(~ aov(DISTANCE ~ DIRECTION, data = .)) %>% 
  map(~ list(summary(.), etaSquared(.))) 

```

# Step 5: Conclusion

I found a significant interaction such that when you are facing towards the target you rate the target as closer than when you are facing away from the target. Additionally, the post-hoc comparison eta-squareds were equivalent to the original paper.

This reproducibility check was a partial success. I managed to get the same model values despite the paper reporting their ANOVA levels incorrectly and having to determine which ANOVA type they used through trial and error. However, I am not sure why the standard error bars in the plot don't match the ones from their paper. It's possible that they are supposed to be 95% CI bars however the STG station traveling West CI looks slightly low. It is hard to say for sure since the original paper does not include y-axis ticks on their plot.



```{r}
reportObject <- reportObject %>%
  filter(dummyRow == FALSE) %>% # remove the dummy row
  select(-dummyRow) %>% # remove dummy row designation
  mutate(articleID = articleID) %>% # add variables to report 
  select(articleID, everything()) # make articleID first column

# decide on final outcome
if(any(reportObject$comparisonOutcome %in% c("MAJOR_ERROR", "DECISION_ERROR"))){
  finalOutcome <- "Failure"
}else{
  finalOutcome <- "Success"
}

# collate report extra details
reportExtras <- data.frame(articleID, pilotNames, copilotNames, pilotTTC, copilotTTC, pilotStartDate, copilotStartDate, completionDate, finalOutcome)

# save report objects
if(reportType == "pilot"){
  write_csv(reportObject, "pilotReportDetailed.csv")
  write_csv(reportExtras, "pilotReportExtras.csv")
}

if(reportType == "copilot"){
  write_csv(reportObject, "copilotReportDetailed.csv")
  write_csv(reportExtras, "copilotReportExtras.csv")
}
```

# Session information

```{r session_info, include=TRUE, echo=TRUE, results='markup'}
devtools::session_info()
```
